diffusion, websites with 1 pc

### 2022-05-27 src/hex_heatmaps.Rmd
betas

    #stat_binhex(bins=150) +
    stat_binhex(aes(fill=log(..count..)), bins=150) +
    geom_polygon(data = gb.df, aes(x=long, y = lat, group = group), #gb.df
                 fill=NA, color = "black", size = 0.1, alpha = 0.8)+
    scale_fill_gradientn(colours=c('light gray','blue'),
                         name='Frequency',na.value=NA) + #, trans = "log10") +
    coord_equal() +
    labs(x=NULL, y=NULL) +
    geom_point(data = cities, aes(x=long, y=lat), colour = "black", size = .1) + 
    geom_text(size = 2, check_overlap = F, nudge_y = .2, data = cities, aes(x=long, y=lat, label = name)) +
    #theme(legend.key.size = unit(0.05, "cm")) + # legend.key.width=unit(1, "cm"), 
    ggmap::theme_nothing(legend = T) +
    theme(legend.title=element_text(size=5.5), legend.text=element_text(size=4)) +
    #theme(legend.position=c(0.075,0.28))
    guides(fill = guide_colorbar(barwidth = 0.5, barheight = 2.5)) +
    ggtitle(t)
  ggsave(p, filename = paste(path.out, t, ".png", sep = ""))
}
```

>>>>

    #stat_binhex(bins=150) +
    stat_binhex(aes(fill=log(..count..)), bins=150) +
    geom_polygon(data = gb.df, aes(x=long, y = lat, group = group), #gb.df
                 fill=NA, color = "black", size = 0.1, alpha = 0.8)+
    scale_fill_gradientn(colours=c('light gray','blue'),
                         name='log(Frequency)',na.value=NA) + #, trans = "log10") +
    coord_equal() +
    labs(x=NULL, y=NULL) +
    geom_point(data = cities, aes(x=long, y=lat), colour = "black", size = .1) + 
    geom_text(size = 2, check_overlap = F, nudge_y = .2, data = cities, aes(x=long, y=lat, label = name)) +
    #theme(legend.key.size = unit(0.05, "cm")) + # legend.key.width=unit(1, "cm"), 
    ggmap::theme_nothing(legend = T) +
    theme(legend.title=element_text(size=5.5), legend.text=element_text(size=4)) +
    #theme(legend.position=c(0.075,0.28))
    guides(fill = guide_colorbar(barwidth = 0.5, barheight = 2.5)) +
    ggtitle(t)
  ggsave(p, filename = paste(path.out, t, ".png", sep = ""))
}
```

### 2022-05-27 src/level_lisa_oa.Rmd
betas

library(tidyverse)
library(rprojroot)
library(rgdal)
library(rgeos)
library(spdep)
library(tmap)
library(maptools)
library(knitr)
library(REAT)
library(tidygeocoder)
library(geosphere)

@@

```{r}
path.lookup <- paste0(path,"/data/raw/PCD_OA_LSOA_MSOA_LAD_AUG21_UK_LU.csv")
lookup <- read_csv(path.lookup) %>% 
  select(pcds, oa11cd) %>% 
  dplyr::rename(pc = pcds)
#glimpse(lookup)
# The problems refer to Welsh LAD names. Not a problem for the analysis.
#sapply(lookup, function(x) sum(is.na(x)))
# 10332 missing msoa11cd
```

@@

#path.out <- paste0(path, "/outputs/lisa_level_pc", n, "_oa") # for unique PC
path.out <- paste0(path, "/outputs/lisa_level_pc", m, "_oa")  # for multiple PC

@@

```{r}
morani %>% as_tibble() %>% 
  rename('morani'=V1,
                   p = V2,
                   year = V3) %>% 
  kable()

@@

for (t in 1996:2012){
    a <- df %>% filter(year==t)
  b <- as.data.frame(gini(a$n))
  b$year = t
  gini.df <- rbind(gini.df, b)
}
```

@@

# Minimum distance 
dist.retail <- transform(dist.retail, dist.retail = do.call(pmin, dist.retail[-1]))
dist.retail <- dist.retail %>% select(oa11cd, dist.retail)

@@

names(dens.London)[1] <- "rsquared"
ggplot(dens.London) +
  geom_line(aes(x=year, y = rsquared))

library(broom)
out.model <- out.model %>% 
  mutate(year = 1996:2012)

ggplot(out.model, aes(x=reorder(year, year), y=estimate)) +
#ggplot(out.model, aes(x=year, y = estimate)) +  
           geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                       width = 0.2,size  = 1,
                       position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip() 
```

@@

names(dens.distMet)[1] <- "rsquared"
ggplot(dens.distMet) +
  geom_line(aes(x=year, y = rsquared))

@@

ggplot(out.modelMet, aes(x=reorder(year, year), y=estimate)) +
           geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                       width = 0.2,size  = 1,
                       position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip() 
```

@@

names(dens.dist.retail)[1] <- "rsquared"
ggplot(dens.dist.retail) +
  geom_line(aes(x=year, y = rsquared))

@@

ggplot(out.model.retail, aes(x=reorder(year, year), y=estimate)) +
           geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                       width = 0.2,size  = 1,
                       position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip()

@@

>>>>

library(tidyverse)
library(rprojroot)
library(rgdal)
library(rgeos)
library(spdep)
library(tmap)
library(maptools)
library(knitr)
library(REAT)
library(tidygeocoder)
library(geosphere)
library(broom)

@@

```{r}
path.lookup <- paste0(path,"/data/raw/PCD_OA_LSOA_MSOA_LAD_AUG21_UK_LU.csv")
lookup <- read_csv(path.lookup) %>% 
  dplyr::select(pcds, oa11cd) %>% 
  dplyr::rename(pc = pcds)
#glimpse(lookup)
# The problems refer to Welsh LAD names. Not a problem for the analysis.
#sapply(lookup, function(x) sum(is.na(x)))
# 10332 missing msoa11cd
```

@@

path.out <- paste0(path, "/outputs/lisa_level_pc", n, "_oa") # for unique PC
#path.out <- paste0(path, "/outputs/lisa_level_pc", m, "_oa")  # for multiple PC

@@

```{r}
path.out <- paste0(path, "/outputs/morani.csv")
morani %>% as_tibble() %>% 
  rename('morani'=V1,
                   p = V2,
                   year = V3) %>% 
  kable() #%>% 
  #write_csv(path.out)

@@

for (t in 1996:2012){
    a <- df %>% filter(year==t)
  b <- as.data.frame(gini(a$n))
  b$year = t
  gini.df <- rbind(gini.df, b)
}

path.out <- paste0(path, "/outputs/gini.csv")
gini.df %>% write_csv(path.out)
```

@@

# Minimum distance 
dist.retail <- transform(dist.retail, dist.retail = do.call(pmin, dist.retail[-1]))
dist.retail <- dist.retail %>% dplyr::select(oa11cd, dist.retail)

@@

names(dens.London)[1] <- "rsquared"

path.out <- paste0(path,"/outputs/rsq_dist_london.png")
ggplot(dens.London) +
  geom_line(aes(x=year, y = rsquared)) +
  ylab("Rsquared") + 
  ggtitle("Regression fit, distance to London on website density") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggsave(path.out)

out.model <- out.model %>% 
  mutate(year = 1996:2012)

path.out <- paste0(path,"/outputs/b_dist_london.png")
ggplot(out.model, aes(x=reorder(year, year), y=estimate)) +
#ggplot(out.model, aes(x=year, y = estimate)) +  
           geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                       width = 0.2,size  = 1,
                       position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip() +
  ylab("distance coefficient") + xlab("") + 
  ggtitle("Regression coefficients, distance to London on website density") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggsave(path.out)
```

@@

names(dens.distMet)[1] <- "rsquared"

path.out <- paste0(path,"/outputs/rsq_dist_city.png")
ggplot(dens.distMet) +
  geom_line(aes(x=year, y = rsquared)) +
  ylab("Rsquared") + 
  ggtitle("Regression fit, distance to nearest city on website density") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggsave(path.out)

@@

path.out <- paste0(path,"/outputs/b_dist_city.png")
ggplot(out.modelMet, aes(x=reorder(year, year), y=estimate)) +
           geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                       width = 0.2,size  = 1,
                       position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip() +
  ylab("distance coefficient") + xlab("") + 
  ggtitle("Regression coefficients, distance to nearest city on website density") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggsave(path.out)
```

@@

names(dens.dist.retail)[1] <- "rsquared"

path.out <- paste0(path,"/outputs/rsq_dist_centre.png")
ggplot(dens.dist.retail) +
  geom_line(aes(x=year, y = rsquared)) +
  ylab("Rsquared") + 
  ggtitle("Regression fit, distance to nearest retail centre on website density") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggsave(path.out)

@@

path.out <- paste0(path,"/outputs/b_dist_centre.png")
ggplot(out.model.retail, aes(x=reorder(year, year), y=estimate)) +
           geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                       width = 0.2,size  = 1,
                       position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip() +
  ylab("distance coefficient") + xlab("") + 
  ggtitle("Regression coefficients, distance to nearest city on website density") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggsave(path.out)

@@

## The below are unfinished
